---
title: "Recurrence Decision Report"
format: html
execute: 
  echo: false
  warning: false
  message: false
---

```{r}

# required R packages

## comment it out if you only want to redner .qmd directly or run the code quarto::quarto_render("report/decision_report.qmd") for preview, otherwise, keep it as it is if you want to execute the whole project via tar_make() in the console
# setwd("..")

library(targets)
library(dplyr)

# load outputs

decision_output_cont <- tar_read(decision_output_cont)
decision_output_cate <- tar_read(decision_output_cate)

validation_cont <- tar_read(validation_cont)
validation_cate <- tar_read(validation_cate)

evaluate_cont <- tar_read(evaluate_cont)
evaluate_cate <- tar_read(evaluate_cate)

```

# 1. Executive Summary

This report presents the result of a recurrence prediction pipeline, including model outputs, validation checks, and decision-support segmentation. The key highlights are listed below:

- Recurrence risk was estimated using logistic regression models
- The population was segmented into risk tiers (high, medium, low)
- Suggested actions were assigned to support prioritisation
- Validation checks were performed to ensure output reliability

# 2. Model Performance

Two model specifications were evaludated:

- Model A: continuous duration representation

```{r}
evaluate_cont
```

- Model B: categorical duration representation

```{r}
evaluate_cate
```

# 3. Validation Checks

The following checks were performed on prediction outputs to ensure data quality and logical reliability.

- Required columns present
- No unexpected missing values
- Predicted probabilities within [0,1]
- Predicted classes valid (0/1)
- Risk level values valid

For Model A, the checks are:

```{r}
validation_cont
```
, and for Model B:
```{r}
validation_cate
```

# 4. Decision Output Overview

Predicted probablities were translated into actionable risk tiers:

- High risk indicates priority to follow-up
- Medium risk suggests an action of monitoring
- Low risk advises routine review

The distribution of risk tiers and the first 10 top high-risk cases based on Model A are:
```{r}

decision_output_cont |>
  count(risk_tier)

top_high_count_cont <- decision_output_cont |>
  filter(risk_tier == "high") |>
  arrange(desc(pred_prob)) |>
  head(10)

if(nrow(top_high_count_cont) == 0){
  
  cat("No high-risk cases identified under Model A, indicating the prediction of this model is relatively conservative.")
  
} else {
  
  top_high_count_cont
  
}

```

, and based on Model B are:
```{r}
decision_output_cate |>
  count(risk_tier)


top_high_count_cate <- decision_output_cate |>
  filter(risk_tier == "high") |>
  arrange(desc(pred_prob)) |>
  head(10)

if(nrow(top_high_count_cate) == 0){
  
  cat("No high-risk cases identified under Model B, indicating the prediction of this model is relatively conservative.")
  
} else {
  
  top_high_count_cate
  
}

```

# 5. Interpretation

The model outputs are intended to support prioritisation decisions rather than to provide deterministic predictions.

Here are key considerations:

- Risk tiers are based on probability thresholds and should be interpreted alongside contextual information.

- High-risk cases indicate higher likelihood of recurrence within the predefined time window.

- The models are designed for demonstration using simulated data and does not represent real-world intervention effectiveness.

# 6. Limitations

The project has limitations listed below:

- The data used in this work is simulated.
- Recurrence is driven primarily by risk level in the data generating process.
- Duration-based features may not reflect real-world signals.
- Thresholds for risk segmentation are illustrative.